---
title       : Predict children's height from parents' height
subtitle    : A simple linear regression model 
author      : Clark Keint
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Galton's Data

1. The Data set from tabulated data set used by Galton in 1885 to study the relationship between a parent's height and their childrens.
2. This data is used to predict childrens' height by their parents' height.
3. The data frame has 928 observations on the following 2 variables:
   * child  : The child's height
   * parent : The “midparent” height
4. There is a Correction for gender via multiplying female heights by 1.08.


--- .class #3 

## Histogram of two variable
```{r,fig.height=4.5,fig.width=10}
library(UsingR); data(galton)
par(mfrow=c(1,2))
hist(galton$child,col="blue",breaks=100)
hist(galton$parent,col="blue",breaks=100)
```

--- .class #4 

## Comparing children's heights and their parents' heights
```{r,fig.height=5.0,fig.width=13,echo=FALSE}
par(mfrow=c(1,2)); 
plot(galton$parent,galton$child,pch=19,col="blue")
points(mean(galton$parent), mean(galton$child), col='red',cex = 2, pch = 19)
freqData <- as.data.frame(table(galton$child, galton$parent))
names(freqData) <- c("child", "parent", "freq")
plot(as.numeric(as.vector(freqData$parent)), as.numeric(as.vector(freqData$child)),
     pch = 21, col = "black", bg = "lightblue", cex = .15 * freqData$freq, 
     xlab = "parent", ylab = "child")
points(mean(galton$parent), mean(galton$child), col='red',cex = 2, pch = 19)
```
* Size of point in figure 2 represents number of points at that (X, Y) combination.
* Red point are mean value of two variable.

---  .class #5 
## Use the simple linear regression to fit a line 
```{r}
fit <- lm(child ~ parent,data=galton);
fit$coefficients
```
```{r,fig.height=4.8,fig.width=7,echo=FALSE}
plot(as.numeric(as.vector(freqData$parent)), as.numeric(as.vector(freqData$child)),
     pch = 21, col = "black", bg = "lightblue", cex = .15 * freqData$freq, 
     xlab = "parent", ylab = "child")
points(mean(galton$parent), mean(galton$child), col='red',cex = 2, pch = 19)
lines(galton$parent,fit$fitted,col="red",lwd=3)
```

---  .class #6
## Predict children's height from parents' height
```{r}
parent_height <- 66
prediction <- predict(fit, newdata = data.frame(parent=c(parent_height)))
prediction[[1]]
```

```{r,fig.height=4.8,fig.width=7,echo=FALSE}
plot(as.numeric(as.vector(freqData$parent)), as.numeric(as.vector(freqData$child)),
     pch = 21, col = "black", bg = "lightblue", cex = .15 * freqData$freq, 
     xlab = "parent", ylab = "child")
lines(galton$parent,fit$fitted,col="red",lwd=3)
points(parent_height, prediction, col='blue',cex = 2, pch = 19)      
lines(c(parent_height,parent_height),c(60,prediction),col="blue",lwd=1)
lines(c(60,parent_height),c(prediction,prediction),col="blue",lwd=1)
points(mean(galton$parent), mean(galton$child), col='red',cex = 2, pch = 19)
```
